\tool: Revisiting BadUSB with Type-C

### 2021-03-06 WOOT/Files/related_work.tex
fix related work

% USB protocol attacks
In the field of USB security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the USB protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to pretend like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
support video transmission, there exists a protocol called MHL (Mobile
High-Definition Link) which extends the USB standard and allows the video signal to
be transmitted through the USB interface. JFC~\cite{JFC}, short for juicy filming
charging is such a work that abuses this standard and exfiltrate video data
from the victim without permission. However, in JFC, this data exfiltration is not
combined with BadUSB attacks, and MHL is an outdated standard, which limits its
capability.

@@

It is worth noting that our \tool is different from JFC~\cite{JFC}. Firstly, Juice Filming Attacks can not control the attacked device, but can only video-capture user inputs during charging. However, our \tool can monitor the screen at the same time as controling the attacked device, which enhances the efficiency of stealing users’ private data. Second, we design an prototype to attack in real time remotely. Third, the scope of \tool is wider, \tool also poses a threat to laptops that charged with use USB-C interface.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected for making a different claim 
that does not match the authorization results. USBeSafe\cite{usbesafe} analyses the 
feature vector constructed from with data collected from USB Request Block(URBs), 
it would detect the novel USB packets based on the machine learning algorithm and send 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFC (Juicy Film Charging)~\cite{JFC} which abuses the MHL
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attacks.

@@

>>>>

% USB protocol attacks
In the field of USB security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the USB protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to pretend like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
support video transmission, there exists a protocol called MHL (Mobile
High-Definition Link) which extends the USB standard and allows the video signal to
be transmitted through the USB interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is such a work that abuses this standard and exfiltrate video data
from the victim without permission. However, in JFC, this data exfiltration is not
combined with BadUSB attacks, and MHL is an outdated standard, which limits its
capability.

@@

It is worth noting that our \tool is different from JFC~\cite{JFC}. Juice Filming Attacks can not control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

@@

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decides whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected for making a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed from with data collected from USB Request Block(URBs), 
it would detect the novel USB packets based on the machine learning algorithm and send 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFC~\cite{JFC} which abuses the MHL
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attacks.

@@

		\makecell{USBeSafe~\cite{usbesafe}} & \makecell*[c]{\circleempty} & \circlefull & \circlefull &\circlefull& \circlefull\\
		\hline

		\makecell{Mueller \emph{et al.}~\cite{MuellerZN19}} & \makecell*[c]{\circleempty} & \circlefull & \circlefull &\circlehalf& \circlefull\\
		\hline
